---
title: "Spatial Techniques In R"
author: "Robert McGuinn"
date: "March 22, 2018"
output:
  html_document:
    toc: true
    toc_float: true
    toc_depth: 2
    theme: paper
    highlight: default
    
  
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, message = FALSE, warning = FALSE)
```
"C:/Program Files/RStudio/bin/pandoc/pandoc" +RTS -K512m -RTS index.utf8.md --to html4 --from markdown+autolink_bare_uris+ascii_identifiers+tex_math_single_backslash --output index.html --smart --email-obfuscation none --self-contained --standalone --section-divs --table-of-contents --toc-depth 2 --variable toc_float=1 --variable toc_selectors=h1,h2 --variable toc_collapsed=1 --variable toc_smooth_scroll=1 --variable toc_print=1 --template 
"C:/Program Files/RStudio/bin/pandoc/pandoc" +RTS -K512m -RTS index.utf8.md --to html4 --from markdown+autolink_bare_uris+ascii_identifiers+tex_math_single_backslash --output index.html --smart --email-obfuscation none --self-contained --standalone --section-divs --table-of-contents --toc-depth 2 --variable toc_float=1 --variable toc_selectors=h1,h2 --variable toc_collapsed=1 --variable toc_smooth_scroll=1 --variable toc_print=1 --template
"C:/Program Files/RStudio/bin/pandoc/pandoc" +RTS -K512m -RTS index.utf8.md --to html4 --from markdown+autolink_bare_uris+ascii_identifiers+tex_math_single_backslash --output index.html --smart --email-obfuscation none --self-contained --standalone --section-divs --table-of-contents --toc-depth 2 --variable toc_float=1 --variable toc_selectors=h1,h2 --variable toc_collapsed=1 --variable toc_smooth_scroll=1 --variable toc_print=1 --template 

# This

"C:/Program Files/RStudio/bin/pandoc/pandoc" +RTS -K512m -RTS index.utf8.md --to html4 --from markdown+autolink_bare_uris+ascii_identifiers+tex_math_single_backslash --output index.html --smart --email-obfuscation none --self-contained --standalone --section-divs --table-of-contents --toc-depth 2 --variable toc_float=1 --variable toc_selectors=h1,h2 --variable toc_collapsed=1 --variable toc_smooth_scroll=1 --variable toc_print=1 --template 
"C:/Program Files/RStudio/bin/pandoc/pandoc" +RTS -K512m -RTS index.utf8.md --to html4 --from markdown+autolink_bare_uris+ascii_identifiers+tex_math_single_backslash --output index.html --smart --email-obfuscation none --self-contained --standalone --section-divs --table-of-contents --toc-depth 2 --variable toc_float=1 --variable toc_selectors=h1,h2 --variable toc_collapsed=1 --variable toc_smooth_scroll=1 --variable toc_print=1 --template
"C:/Program Files/RStudio/bin/pandoc/pandoc" +RTS -K512m -RTS index.utf8.md --to html4 --from markdown+autolink_bare_uris+ascii_identifiers+tex_math_single_backslash --output index.html --smart --email-obfuscation none --self-contained --standalone --section-divs --table-of-contents --toc-depth 2 --variable toc_float=1 --variable toc_selectors=h1,h2 --variable toc_collapsed=1 --variable toc_smooth_scroll=1 --variable toc_print=1 --template 


## This other thing

"C:/Program Files/RStudio/bin/pandoc/pandoc" +RTS -K512m -RTS index.utf8.md --to html4 --from markdown+autolink_bare_uris+ascii_identifiers+tex_math_single_backslash --output index.html --smart --email-obfuscation none --self-contained --standalone --section-divs --table-of-contents --toc-depth 2 --variable toc_float=1 --variable toc_selectors=h1,h2 --variable toc_collapsed=1 --variable toc_smooth_scroll=1 --variable toc_print=1 --template 
"C:/Program Files/RStudio/bin/pandoc/pandoc" +RTS -K512m -RTS index.utf8.md --to html4 --from markdown+autolink_bare_uris+ascii_identifiers+tex_math_single_backslash --output index.html --smart --email-obfuscation none --self-contained --standalone --section-divs --table-of-contents --toc-depth 2 --variable toc_float=1 --variable toc_selectors=h1,h2 --variable toc_collapsed=1 --variable toc_smooth_scroll=1 --variable toc_print=1 --template
"C:/Program Files/RStudio/bin/pandoc/pandoc" +RTS -K512m -RTS index.utf8.md --to html4 --from markdown+autolink_bare_uris+ascii_identifiers+tex_math_single_backslash --output index.html --smart --email-obfuscation none --self-contained --standalone --section-divs --table-of-contents --toc-depth 2 --variable toc_float=1 --variable toc_selectors=h1,h2 --variable toc_collapsed=1 --variable toc_smooth_scroll=1 --variable toc_print=1 --template 

https://github.com/positivebob/out/blob/gh-pages/code/main.R


### This other thing alone    


```{r install}


##### install packages #####
library(sp)
library(rgdal)
library(dplyr)
library(rmarkdown)
# library(maptools)
# library(ggplot2)
# library(rgeos)
# library(ggmap)
# library(dplyr)
# library(lazyeval)
```

# Quarterly Results {.tabset}

## By Product

Stuff about the product

## By Region

Stuff about the region

# Yo
